---
title: Assignment2.Exercise3
output: github_document
editor_options: 
  chunk_output_type: console
---

<!-- README.md is generated from README.Rmd. Please edit that file -->

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>",
  warnings = FALSE, 
  messages = FALSE, 
  prompt = FALSE,
  fig.path = "man/figures/README-",
  out.width = "100%"
)

```



<!-- badges: start -->

<!-- badges: end -->

This R package is designed to simulate how customers will go through a first come, first serve queuing system as long as “fate” has already decided when each customer will arrive and their service times. 

## First things first

`assignment2.exercise3` is a toy project and is still under development. You can install the latest version from [GitHub](https://github.com/) with:

```{r, install, results = "hide", eval = FALSE}
# install.packages("remotes")
remotes::install_github("hemishahuja140/assignment2.exercise3")
```

## Take it for a spin

`assignment2.exercise3` contains one function only. `Multiserver()` will calculate the times at which each customer’s service time starts and end.

```{r example}
devtools::install_github("https://github.com/hemishahuja140/assignment2.exercise3.git")

library("assignment2.exercise3")
 
Multiserver(12.2,9.8,1) 
```

Alternatively, you can supply the input values from the bank datset within the package

```{r, customise}
Multiserver(bank$arrival_time[3],bank$service_time[9])
```









